---
title: "Inshore density calculations"
author: "MZD"
date: "4/15/2020"
output: html_document
---

```{r}
library(tidyverse)
library(lubridate)
```

Load data
```{r}
tx.catch <- read_csv("raw/tpwd-trawl-catch.csv")
tx.lengths <-read_csv("raw/tpwd-trawl-lengths.csv")
```

```{r}
tx.catch
tx.lengths
```

Need to convert dttm into datetime, create year, month, sample ID columna:
```{r}
tx.catch <- tx.catch %>% 
  mutate(dt = dmy_hms(completion_dttm)) %>% 
  mutate(year = year(dt)) %>% 
  mutate(month = month(dt)) %>% 
  mutate(trawl_id = paste(major_area_code,station_code,date(dt),sep = "-"))
tx.catch
```

```{r}
tx.lengths <- tx.lengths %>% 
  mutate(dt = dmy_hms(completion_dttm)) %>% 
  mutate(year = year(dt)) %>% 
  mutate(trawl_id = paste(major_area_code,station_code,date(dt),sep = "-"))
tx.lengths
```

In lengths dataset, set maturity stage code as factor and classify as mature or not (mature_female) and ovigerous or not (ovigerous):
```{r}
tx.lengths <- tx.lengths %>% 
  mutate(maturity_stage_code = factor(maturity_stage_code)) %>% 
  mutate(mature_female = recode(maturity_stage_code, 
                           "1" = "N",
                           "2" = "Y",
                           "3" = "Y",
                           "4" = "Y",
                           "5" = "N",
                           "6" = "N",
                           "0" = "N",
                           "8" = "Y",
                           "9" = "N")) %>%
  mutate(ovigerous = recode(maturity_stage_code, 
                           "1" = "N",
                           "2" = "N",
                           "3" = "Y",
                           "4" = "Y",
                           "5" = "N",
                           "6" = "N",
                           "0" = "N",
                           "8" = "N",
                           "9" = "N"))
tx.lengths
```
```{r}
table(tx.lengths$mature_female)
```

Count how many mature females in each sample, create new dataframe:
```{r}
mat.fem.counts<- tx.catch %>% 
  full_join(tx.lengths, by = "trawl_id") %>% 
  filter(mature_female == "Y") %>% 
  group_by(trawl_id) %>% 
  tally() %>% 
  rename(mature_females = n)
mat.fem.counts
```

```{r}
sum(mat.fem.counts$mature_females)
```

Now same for ovigerous females:
```{r}
ovig.counts<- tx.catch %>% 
  full_join(tx.lengths, by = "trawl_id") %>% 
  filter(ovigerous == "Y") %>% 
  group_by(trawl_id) %>% 
  tally() %>% 
  rename(ovigerous = n)
ovig.counts
```
```{r}
sum(ovig.counts$ovigerous)
```


Now join mature female and ovig female dataframes to tx.catch, mature females to crabs/ha based on 4.8 km/hr tow speed and 6.1-m trawl width, as follows:
mature females per hectare = (# of mature females caught) /
     (6.1 m trawl width) * (4800 m/hr speed) * (elapsed_time in h) * (1 hectare/ 10,000 m^2)
```{r}
tx.catch <- tx.catch %>% 
  left_join(mat.fem.counts, by = "trawl_id") %>% 
  left_join(ovig.counts, by = "trawl_id") %>%
  mutate(mature_females = replace_na(mature_females, 0)) %>% 
  mutate(ovigerous = replace_na(ovigerous, 0)) %>% 
  mutate(matfem_per_ha = mature_females / (6.1*4800*elapsed_time/10000))
tx.catch
```
```{r}
sum(tx.catch$mature_females)
sum(tx.catch$ovigerous)
```

Check catch per sample for 2006-2016, see if appx. matches Anderson et al. 2017 (0.024 ovigerous per sample):
```{r}
tx.catch %>% 
  filter(year < 2017) %>% 
  summarise(mean.mature = mean(mature_females), mean.ovigerous = mean(ovigerous)) 

```

Summarize catch by month:
```{r}
months<- tx.catch %>% 
 group_by(month) %>% 
 summarise(mean.mature = mean(mature_females), mean.ovigerous = mean(ovigerous)) 
months
```

```{r}
plot(months$month, months$mean.mature)
plot(months$month, months$mean.ovigerous)
```

Write to CSV:
```{r}
write_csv(tx.catch,"generated/tx-catch-matfem.csv")
write_csv(tx.lengths,"generated/tx-lengths.csv")

```


#QGIS processing

Land layer = /Users/mzd/The University of Southern Mississippi/Craboratory - Documents/gis-layers/Shorelines_Landcovers/GSHHS_shoreline/GSHHS_f_GOM-conus-albers.shp

Processing documented in /Users/mzd/Dropbox (The Craboratory)/RESEARCH/projects/seamap_2017/data-and-analyses/Inshore-cpue/gis/tx-inshore-cpue-calcs.model3

Could use only peak spawning grounds, but most appropriate to use full estuarine area (total major bay area):

#Back to R
```{r}
major.bays <- read_csv("raw/major-bays.csv")
```

Calculate mean mature female catch per ha and total # of mature female crabs in TX estuarine waters per year, based on all months:
```{r}
tx.annual.crabs <- tx.catch %>% 
  filter(major_area_code < 17) %>% #limits to only the estuarine bays, not the offshore areas
  group_by(year) %>% 
  summarise(mean.mat.cpue = mean(matfem_per_ha)) %>% 
  mutate(total = mean.mat.cpue * sum(major.bays$Hectares)) 
tx.annual.crabs

```

Calculate total based only on June and July in all major bays:
```{r}
tx.mo.crabs <- tx.catch %>% 
  filter(major_area_code < 17) %>% 
  filter(month == 6 | month ==7) %>% 
  group_by(year) %>% 
  summarise(mean.mat.cpue = mean(matfem_per_ha)) %>% 
  mutate(total = mean.mat.cpue * sum(major.bays$Hectares)) 
tx.mo.crabs
```










